Delocalization of Eigenvectors in Random Matrices

### 2025-03-23 Draft.tex
stochastic domination product

\subsection{Continuity Argument}
Having established the stochastic bound on the individual derivatives, we can now lay out the continuity argument that will allows us to preserve control throughout the entire replacement. To start, define the following:

@@

\begin{boxtheorem}{Lemma A5: (Large Deviation estimates)}   (Theorem 7.7 \cite{dynamic}) \label{lemma-a5}

@@

@@

\begin{boxt}{Lemma B.2} \label{lemma-b2}
(Result $4.6ri$ \cite{bandSDE})
$$\max_{x, y} |G_{xy} - \delta_{xy}m(z)|\lesssim W^{-\frac{1}{2}} \eta_s^{-\frac{1}{4}}
$$
\end{boxt}

>>>>

\subsection{Continuity Argument}
With the completed bound on the functional expression of derivatives, we can now construct the continuity argument. We will assume minimal resolvent bounds, namely that $|\tilde{G}_{k\ell}|\prec 1$ for all $k, \ell\in \{1, \cdots, N\}$.

Having established the stochastic bound on the individual derivatives, we can now lay out the continuity argument that will allows us to preserve control throughout the entire replacement. To start, define the following:

@@

\begin{boxtheorem}{Lemma A5: (Large Deviation estimates)}    \label{lemma-a5}

@@

\end{boxtheorem}
\textit{Proof} - can be found as Theorem 7.7 in Yau's Dynamic RMT textbook \cite{dynamic}.

\begin{boxtheorem}{Lemma A6: (Stochastic Domination Product)}\label{lemma-a6}

If $X_i \prec Y_i$ for $i = 1,2,...,\ell$, then $\prod_{i=1}^{\ell} X_i \prec \prod_{i=1}^{\ell} Y_i$.
\end{boxtheorem}
\textit{Proof} - By definition, for any $\epsilon, D > 0$, there exist $N_{\epsilon,D,i}$ such that: $$\sup_{s\in S_N}\mathbb{P}\left(X_i(s) > N^{\epsilon/\ell} Y_i(s)\right) < N^{-(D+\log_N \ell)}$$ for all $N \geq N_{\epsilon,D,i}$. For the product, consider: $$\mathbb{P}\left(\prod_{i=1}^{\ell} X_i(s) > N^{\epsilon} \prod_{i=1}^{\ell} Y_i(s)\right).$$
This event occurs only if at least one $X_i(s) > N^{\epsilon/\ell} Y_i(s)$. By the union bound: $$\mathbb{P}\left(\prod_{i=1}^{\ell} X_i(s) > N^{\epsilon} \prod_{i=1}^{\ell} Y_i(s)\right) \leq \sum_{i=1}^{\ell} \mathbb{P}\left(X_i(s) > N^{\epsilon/\ell} Y_i(s)\right) < \ell \cdot N^{-(D+\log_N \ell)} = N^{-D}$$ for all $N \geq \max_{i=1}^{\ell} N_{\epsilon,D,i}$.

@@

\begin{boxt}{Lemma B.2} \label{lemma-b2}
(Result $4.6$ \cite{bandSDE})
$$\max_{x, y} |G_{xy} - \delta_{xy}m(z)|\lesssim W^{-\frac{1}{2}} \eta_s^{-\frac{1}{4}}
$$
\end{boxt}
